Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-02-03 docs/msr.tex
Introduction: some changes - fixes

A security bug is a programming error that introduces a potentially
exploitable weakness into a computer system~\cite{SSL12}. This weakness could lead to a
security breach with unfortunate consequences in different layers, like databases,
native code, applications, libraries and others. Despite the significant
effort to detect and eliminate such bugs~\cite{SZ12}, little attention has been paid to
study them in relation to software evolution~\cite{L96, LRWPT97, IB06}. In this paper we present how we
used a large software ecosystem to analyze how evolving software packages are
related to the different types of software vulnerabilities.

One of the most common approaches to identify software vulnerabilities is
{\it static analysis}~\cite{CW07}. This kind of analysis involves the
inspection of the program's source or object code without executing
it. For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
a popular static analysis tool that has already been used in
research~\cite{AP10, HP07, HP04}. Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the Maven\footnote{\url{http://maven.apache.org/}}
repository (approximately 265GB of data). Then we observed the changes that
involved the security bugs and their characteristics. This research builds upon
our earlier work on the topic~\cite{MGS12}.

We chose to focus our study on the security bugs rather than other
software bugs because compared to the other software bugs,
security bugs have a distinct feature: they are critical. Specifically, a software bug can
lead to a mulfunction of a software artifact that runs under specific
requirements but a security bug can allow a malicious user to alter the
execution of the entire application. In this case, such bugs could span a wide range
of security and privacy issues, like viewing sensitive information, the destruction or
modification of sensitive data, denial of service and others.
Hence, one of the basic pursuits in every new software release should be the
mitigation of such bugs.

The motivation behind our work is to validate if programmers tend to care for
such high-risk bugs when they release a new version of their software. In
addition, we want to investigate other critical aspects associated with such
vulnerabilities. For instance, we want to elaborate more on the relation of security
bugs not only with performance bugs (as Zaman et al.~\cite{ZAH11} have already
did) but also with other bug categories. In the same manner, we want to check
if the relation between an artifact's size and its' software bugs applies 
to security bugs (citation needed). Finally, the structure of the Maven ecosystem,
gives us the oportunity to see if artifacts that is a dependency to a high
number of other artifacts contains a high rate of security bugs. In this case
we can strenghten the relationship between Linus' Law and software security as
Meneely et al. have already showed~\cite{MW10}.

@@

\begin{itemize}
	\item The analysis of how security bugs evolve in time. To achieve
this, we inspect every project per version. Our hypothesis is that security
bugs must decrease as a project evolves since they are critical and developers
should eliminate them.
	\item We show evidence of the relation between security bugs and the artifact's size.  Here, size is
defined in terms of bytecode.
	\item Security bug persistense between versions. We show evidence that specific bugs are
not eliminated between versions.
	\item The correlation of security bugs with other bug categories. We
show evidence that such bugs are correlated with bugs that have to do with
performance, coding practices and others.
	\item The relation of software dependencies and security bugs. Our
hypothesis is that an artifact that is a dependency of many other artifacts
should have a low rate of security bugs. 
\end{itemize}

>>>>

A security bug is a programming error that introduces a potentially
exploitable weakness into a computer system~\cite{SSL12}. This weakness could lead to a
security breach with unfortunate consequences in different layers, like databases,
native code, applications, libraries and others. Despite the significant
effort to detect and eliminate such bugs~\cite{SZ12}, little attention has been paid to
study them in relation to software evolution~\cite{L96, LRWPT97, IB06}. In this paper we present how we
used a large software ecosystem to analyze how evolving software packages are
related to the different types of security vulnerabilities.

One of the most common approaches to identify security bugs is
{\it static analysis}~\cite{CW07}. This kind of analysis involves the
inspection of the program's source or object code without executing
it. For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
a popular static analysis tool that has already been used in
research~\cite{AP10, HP07, HP04}. Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the Maven\footnote{\url{http://maven.apache.org/}}
repository (approximately 265GB of data). Then we observed the changes that
involved the security bugs and their characteristics. This research builds upon
our earlier work on the topic~\cite{MGS12}.

We chose to focus our study on the security bugs rather than other
software bugs. This is because compared to other bug categories,
the category of security bugs has a distinct feature: it is critical. Specifically, a software bug can
lead to a mulfunction of a software artifact that runs under specific
requirements but a security bug can allow a malicious user to alter the
execution of the entire application. In this case, such bugs could span a wide range
of security and privacy issues, like viewing sensitive information, the destruction or
modification of sensitive data, denial of service and others.
Hence, one of the basic pursuits in every new software release should be the
mitigation of such bugs.

The motivation behind our work is to validate if programmers tend to care for
such high-risk bugs when they release a new version of their software. In
addition, we want to investigate other critical aspects associated with such
vulnerabilities. For instance, we want to elaborate more on the relation of security
bugs not only with performance bugs (as Zaman et al.~\cite{ZAH11} have already
did) but also with other bug categories. In the same manner, we want to check
if the relation between an artifact's size and its' software bugs applies 
to security bugs (citation needed). Finally, the structure of the Maven ecosystem,
gives us the oportunity to see if an artifact that is a dependency to a large
number of other artifacts contains a high rate of security bugs. In this case
we can strenghten the relationship between Linus' Law and software security as
Meneely et al. have already indicated~\cite{MW10}.

@@

\begin{itemize}
	\item The analysis of how security bugs evolve over time. To achieve
this, we inspect every project per version. Our hypothesis is that security
bugs must decrease as a project evolves since they are critical and developers
should eliminate them.
	\item We show evidence of the relation between security bugs and the artifact's size.  Here, size is
defined in terms of bytecode.
	\item Security bug persistense between versions. We show evidence that specific bugs are
not eliminated between versions.
	\item The correlation of security bugs with other bug categories. We
show evidence that such bugs are correlated with bugs that have to do with
performance, coding practices and others.
	\item The relation of software dependencies and security bugs. Our
hypothesis is that an artifact that is a dependency of many other artifacts
should have a low rate of security bugs. 
\end{itemize}
